Abstractions for Type-Level Programming

### 2022-04-07 thesis.tex
Comments
Address Martin's comments on abmiguities

\subsection{Implicit Ambiguities}

@@

\subsection{Implicit Priorities}

When looking for implicits, the Scala compiler visits scopes sequentially, in a precisely defined order.
At any point in the search, if the implicits defined in the subset of scopes considered so far can fulfill the implicit query, the search succeeds and immediately terminates.
This incremental process has two consequences.
First, it allows the compiler to efficiently look for implicits by naturally pruning some of the search space.
Second, it provides an ad-hoc mechanism to disambiguate implicits.
Scala programmer can artificially partition their implicit definitions into multiple scopes to implement a priority system.

@@

% TODO: Add a paragraph about the evolution of the "rule for picking a most specific alternative" during implicit resolution, see https://dotty.epfl.ch/docs/reference/changed-features/implicit-resolution.html

@@

>>>>

\subsection{Implicit Ambiguities}
\label{subsec:implicit-ambiguities}

@@

\subsection{Implicit Priorities}
\label{subsec:implicit-priorities}

When looking for implicits, the Scala compiler visits scopes sequentially, in a precisely defined order.
At any point in the search, if the implicits defined in the subset of scopes considered so far can fulfill the implicit query, the search succeeds and immediately terminates.
This incremental process has two consequences.
First, it allows the compiler to efficiently look for implicits by naturally pruning the search space.
Second, it provides an ad-hoc mechanism to disambiguate implicits.
Scala programmer can artificially partition their implicit definitions into multiple scopes to implement a priority system.

@@

In Scala~3, the rules for implicit ambiguities changed to take implicit parameters into account, thus introducing another, more direct, disambiguation mechanism.
All else being equal, an implicit definition that takes some implicit parameters is considered to be less specific than an implicit definition that takes none~\citep[Changes in Implicit Resolution]{odersky2013scala}.
As a result, implicit-based type-level programs written in Scala~3 do not need to use the patterns of ambiguities and priorities presented in this section (\ref{subsec:implicit-priorities} and \ref{subsec:implicit-ambiguities}).
TODO

@@

% TODO you could write a bit more. Maybe move some of the text of the conclusions of individual chapters there?
